Bayesian Restricted Likelihood Methods: Conditioning on Insufficient Statistics in Bayesian Regression\thanksref{T1}

### 2020-08-15 revision_2/response/responseV3.tex
Revision 2 (#1)
* revision_2 branch to work on BA revisions

* edit ignore file

* added response folder to record our responses

* cleaned aanalysis data to include additional covariates

* edited prior parameters for single group reg. analysis with additional covatiates

* edited prior script for heirarchical set up as well

* clean up prior script to reference a general trend formula for input into lm models

* edited single group reg script to include more covariates

* started simulation with many p

* edits to hierarchical data anlaysis to include extra covariates

* edits to do batch jo

`The proposal is governed by the choice of $p(z^{*})$ and a poor choice could lead to an inefficient MCMC algorithm. For all examples in this paper we defined $p(z^{*})$ to be the uniform distribution on $\mathbb{S}$. The advantage of this choice is that it requires no further tuning parameters.  We have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with a reasonable probability. To implement the method in practice, we generate an n-dimensional independent standard normal $\mb y^{*}$ for the proposal and transform this via $h(\cdot)$. Theoretically, the random normal vector would be projected onto $\mc{C}^{\perp}(X)$ and scaled to unit norm to generate the uniform on $\mathbb{S}$. Using simple algebra and conditions \ref{regEq}-\ref{scaleEq2Reg}, one can show that $h(\cdot)$ is invariant to this projection and scaling. Another option for the proposal suggested by a reviewer that the authors have yet to study is generating a random walk. As we are proposing values on a complicated manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$. This could provide advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.'

@@

\response{For the real data, we have included two additional covariates related to the number of employees at each agency. These were left out originally after EDA revealed their effect sizes were small, but leaving them in makes for a good study as well. We have kept the first simulation as we feel it is a good and simple illustration of the ability to fit hierarchical models with our method. The real data examples now contain a hierarchical example with more covariates. Additionally, we have included a second simulation where the ground truth is a linear regression model with 3 active covariates.  A model with 30 covariates (27 inactive) is fit.  There is correlation amongst some of the covariates, making this problem more realistic.}

@@

\response{As you note, one major advantage is that our method is {\em exactly} a Bayesian method, with $T(y_{obs})$ used in Bayes Theorem to move from prior to posterior.  In a typical setting, under relatively mild conditions on the prior distribution and estimator, Bayesian and frequentist methods will agree asymptotically.  This is reflected in the large-sample central limit theorems (Bayesian and frequentist versions) and is not specially connected to our work.  In this paper, our interest is not in these asymptotic settings where we could simply use a limiting normal distribution as the posterior over the parameters, but rather for the finite sample setting where Bayesian and frequentist methods yield different answers.  The simulations and data analyses document this differential performance.  The standard advantages of Bayes apply -- a guarantee of admissibility from a decision-theoretic view; the ability to combine information across a collection of problems (e.g., the hierarchical setting); and the transition from moment-based methods to likelihood-based methods, for example.  The weaknesses are also there -- a really bad prior distribution produces poor finite-sample performance.  There is a greater computational cost (standard for Bayes vs frequentist), but, given our MCMC routine, no real effort is needed to tune the computation.}

@@

\response{The examples in the paper provide a Bayesian analog of classical robust estimators.  The main disadvantage of our methods relative to the classical estimators is computational.  In Section~3 we detail a data-augmentation MCMC algorithm to fit the models proposed in this paper.  The advantages are those of Bayesian methods.  As is standard for Bayes-classical comparisons, the Bayesian method requires greater computational effort while providing better inference.  As a referee notes, asymptotically, the Bayesian and classical parameter estimates are often very close and have the same limiting posterior variance / sampling variance.  In situations where asymptotic approximation suffices, there is no need to use the computational techniques developed in this paper.'}

@@

\response{This idea is in perfect alignment with our work.  You are right that $T(yobs)$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).  It is merely a statistic upon which we condition when using Bayes Theorem.

@@

For any hope of consistency, the models would need to distinguish between different values of $\theta$, and so a condition along the lines of uniqueness of $E(T(yobs)|\theta)$ in $\theta$ is important.  
}

@@

\response{Thanks for the double check - $C^\perp(X)$ is indeed $n-p$ dimensional.  $\mathcal{A}$ is $n-p-1$ dimensional as one degree of freedom is lost for each coefficient estimate and another degree of freedom is lost for the scale estimate.}

@@

Developing an understanding of sources of variation in the data is important.  In settings where the mechanism that produces bad data is stable, we might even entertain building a model for the bad data as is one tradition in Bayesian statistics.  But there are many instances where modelling the bad data is of little interest.

When we are in a situation where (i) and (ii) hold -- we would argue that this is the usual situation and not the exception -- and we have test data available, there would rarely be any reason to believe that the test data would be pure, consisting only of good data.  This is an important motivator of this work as described in the introduction to our paper.

@@

\response{'The advantages and disadvantages of the method are detailed throughout the paper using simulated and real data. One conceptual advantage of our method is that inferences and predictions are less sensitive to features of the data not captured by
the conditioning statistics than are methods based on the complete likelihood. Choosing statistics targeting the main features of interest allows for inference that focuses on these features. The analysis can help to better understand other features which may not be captured by the conditioning statistics, such as outliers.'}

@@

\response{Thanks for pointing out the wish by some to have default choices for $f$ and $T$.  We consider regression analysis to be so fundamental to the discipline of statsitics and to the practice of data analysis that we feel it inappropriate to specify defaults in a heavy-handed fashion.  This would be much like specifying a default likelihood if one wishes to build a regression model.  Inthe usual regression setting, many would choose to use a constant variance normal likelihood, as we have done in our examples, but we feel it inappropriate to call this a default likelihood.  As you note, choice of the likelihood is part of the analysis when building a Bayesian model.  To this, we add choice of the conditioning statistic $T$ and illustrate the impact of different choices.  Omission of the formal description of the particular M-estimators that we use is an oversight.

We have taken the following steps to address your comment.  We now

\begin{enumerate}
\item Point out that M-estimators have been our default choice in the very first illustrative example:
 \response{Details of these estimators can be found in many places, including \citep{huber2009}. We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers. A short review of these estimators is provided in the Supplementary Material.}
 \item Include a short review of M-estimators in the Supplement
 \item Include `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
\end{enumerate}
}

@@

\response{At the end of Section 3 (note renumbering of sections) we have included a paragraph:}

\response{'Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain. We have found this burden to be marginal in comparison to computing the needed Jacobian. In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.  This is most evident when substantive prior information is available and information in the data is limited.'}

\response{Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages of the new method.}
%}

@@

\response{To address the concern you have raised, we have changed our evaluation metric in the simulation to a closed form version of KL divergence.  We use the KL divergence between two normals: $ 
\log(\hat\sigma_{i}^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma_{i}^{2}}(\sigma^{2} + (\theta_{i} - \hat{\theta_{i}})^{2}
$
While we wouldn't be able to compute this in a real application, it does combines estimation error for both the $\theta_{i}$ and $\sigma$ and is a decent metric to compare the methods under the simulation setup. }
John - I'm puzzled by this one.  I'll have to check the paper when I get dropbox up and running again.  (Steve)

@@

\response{Thanks for noticing this detail. It is most natural if it is mutually absolutely continuous with respect to the distribution induced by the model on S.  For the cases we discuss, this is mutually absolutely continuous with respect to the uniform distribution on S.  We now mention the importance of the support.  We have also included a description of what we use for p throughout based on a previous comment. This comment is after Theorem 4.6.}

@@

\response{Thank you - we believe we have addressed each of these concerns based on the two reviewer's comments. Detailed responses are given above.}

@@

\response{We believe we have addressed similar concerns from the two reviewers - specifically we have included commentary on the advantages and disadvantages of the new method in several places (e.g., see Introduction) as well as some practical recommendations (e.g. See Supplement).}

@@

In contrast, the fractional Bayesian methods do not actually follow Bayes Theorem (there are exceptions in special cases).  Fractional Bayes methods use the theorem as an analogy and so miss many of the benefits of Bayes.  The fractional methods are interesting and they deserve study, but they are not the only solution to Bayesian model misspecification.

In the long run, we suspect that robust and effective Bayesian analyses will make use of ideas from a variety of perspectives that are currently under study.  The various lines of research need groups of researchers investigating them, need time to develop, and they need visibility for the community to appreciate the different perspectives and to develop an understanding of what each brings to the table.}

@@

\response{ Thanks!}

\section{Editor Comments}

@@

\response{Our own training in regression is in the style of ``case analysis'' that has been written about so convincingly by Sandy Weisberg, Dennis Cook, and others.  This training matches your view of strong model diagnostics to identify deficiencies in the model.  A competing type of regression analysis common at the time was developed by Peter Huber, Peter Rousseeuw, and others.  These ``robust regression'' methods seek to automatically discount unusual cases.  Though generally described as a means of handling outliers, many of the popular examples used to illustrate the methods are clearly examples of model misspecification.  The robust methods provide excellent fits for the good (or non-to-mildly misspecified data) when there is misspecification.  Much is known and much has been written about the relative merits of the two styles of regression in various settings.

In the early 1980s, case analysis became the dominant paradigm (though robust regression retained many adherents).  Our natural inclinations match yours for the reasons you give--we would always prefer to build the perfect model.  However, there are a number of reasons why we cannot do so.  These range from the perils of overmodelling (particularly dangerous for Bayesians) to limitations on our ability to identify outliers (from Huber's book, imagine sliding the "y" value for a case from a ridiculous value--surely and outlier--to its case-deleted mean--a zero residual and not identified as an outlier; somewhere along the way, the subjective probability of the case being an outlier must be 0.5 and we would be unable to decide whether the case is an outlier), to our inability to detect modest model misspecification.  Accepting that there are limitations on case analysis and our ability to build the perfect model suggests that we need to develop alternative strategies.  These alternative strategies can even become part of our diagnostic framework:  a discrepancy between the restricted likelihood fit and the traditional Bayesian fit (or predictions) indicates a need for the case-analysis analyst to do more work.

The modern world revolves around large data sets, often with a hierarchical structure.  While case analysis works with data sets of moderate size, it breaks down when one has thousands to millions of cases.  It also breaks down when one is interested in model selection (among a class of models that are, of course, misspecified to some extent) or model averaging.  Robust methods scale much better than case analysis methods do.

The tension between case analysis methods and robust methods is not limited to the regression setting, nor is it limited to merely looking at the fits from the model.  In this work, we lay out the restricted likelihood perspective, develop a computational implementation (as referees and AE note, this development is not trivial), implement the method with code that is available on GitHub, and illustrate some of the benefits of this method relative to standard Bayesian and classical methods.  We view this as an early effort and look to tackle further problems in subsequent papers--in fact, we have given talks about issues such as Bayesian hypothesis testing and model averaging in this framework--and we see a clear path forward for a variety of problems.}

@@

\response{We understand your point of view.  It focuses on dangerous territory for classical statisticans and Bayesians alike.  In keeping with your statement above that *all* models are misspecified (we agree except for a few very simple exceptions--say a single Bernoulli trial), we believe that *all* analyses are compromised.  It is also true that, as soon as one uses diagnostics that have the potential to change the model or the data (removing outliers, for example), the analysis is compromised.  The appropriate likelihood would need to account for all decisions that one might make.  These are two of the arguments made for the use of robust methods (i) that robust estimators reduce the impact of model misspecification, and (ii) that data cleaning and data-based model adjustment destroys the properties of classical tests and Bayesian methods.  It is difficult to quantify these effects, but we have seen them in the practice of data analysis.}

@@

\bibliographystyle{plain}
\bibliography{../bib/refPaper1}

>>>>

`The proposal is governed by the choice of $p(z^{*})$ and a poor choice could lead to an inefficient MCMC algorithm. For all examples in this paper we defined $p(z^{*})$ to be the uniform distribution on $\mathbb{S}$. The advantage of this choice is that it requires no further tuning parameters.  We have noticed good mixing in terms of the ability of the chain to generate new data $\mb y$ that is accepted with a reasonable probability. To implement the method in practice, we generate an n-dimensional independent standard normal $\mb y^{*}$ for the proposal and transform this via $h(\cdot)$. Theoretically, the random normal vector would be projected onto $\mc{C}^{\perp}(X)$ and scaled to unit norm to generate the uniform on $\mathbb{S}$. Using simple algebra and conditions \ref{regEq}-\ref{scaleEq2Reg}, one can show that $h(\cdot)$ is invariant to this projection and scaling. Another option for the proposal suggested by a reviewer that the authors have yet to study is generating a random walk. As we are proposing values on a complex manifold, it might be possible to implement this by conducting the random walk on $\mb y^{*}$ before transforming via $h(\cdot)$. This could provide some advantages in some situations, though we have yet to run into any serious issues with convergence using the independence proposal we utilize here.'

@@

\response{For the real data, we have included two additional covariates related to the number of employees at each agency. These were left out originally after EDA revealed their effect sizes were small, but leaving them in is a good study as well. We have kept the first simulation as we feel it is a good and simple illustration of the ability to fit hierarchical models with our method. The real data examples now contain a hierarchical example with more covariates. Additionally, we have included a second simulation where the ground truth is a linear regression model with 3 active covariates.  A model with 30 covariates (27 inactive) is fit.  There is correlation amongst some of the covariates, making this problem more realistic.}

@@

\response{As you note, one major advantage is that our method is {\em exactly} a Bayesian method, with $T(y_{obs})$ used in Bayes Theorem to move from prior to posterior.  In a typical setting, under relatively mild conditions on the prior distribution and estimator, Bayesian and frequentist methods will agree asymptotically.  This is reflected in the large-sample central limit theorems (Bayesian and frequentist versions) and is not specially connected to our work.  In this paper, our interest is not in these asymptotic settings where we could simply use a limiting normal distribution as the posterior over the parameters, but rather for the finite sample setting where Bayesian and frequentist methods yield different answers.  The simulations and document this differential performance.  The standard advantages of Bayes apply -- a guarantee of admissibility from a decision-theoretic view; the ability to combine information across a collection of problems (e.g., the hierarchical setting); and the transition from moment-based methods to likelihood-based methods, for example.  The weaknesses are also there -- a really bad prior distribution produces poor finite-sample performance.  There is a greater computational cost (standard for Bayes vs frequentist), but, given our MCMC routine, no real effort is needed to tune the computation.}

@@

\response{The examples in the paper provide a Bayesian analog of classical robust estimators.  The main disadvantage of our methods relative to the classical estimators is computational.  In Section~\ref{BayesLinMod} we detail a data-augmentation MCMC algorithm to fit the models proposed in this paper.  The advantages are those of Bayesian methods.  As is standard for Bayes-classical comparisons, the Bayesian method requires greater computational effort while providing better inference.  As a referee notes, asymptotically, the Bayesian and classical parameter estimates are often very close and have the same limiting posterior variance / sampling variance.  In situations where asymptotic approximation suffices, there is no need to use the computational techniques developed in this paper.'}

@@

\response{This is idea is in perfect alignment with our work.  You are right that $T(yobs)$ need not be unbiased -- in fact, it need not even be an estimator (think of sums of squares in an ANOVA setting as opposed to mean squares).  It is merely a statistic upon which we condition when using Bayes Theorem.

@@

For any hope of consistency, the models would need to distinguish between different values of $\theta$, and so a condition along the lines of uniqueness of $E(T(yobs))$ in $\theta$ is important.  
}

@@

\response{Thanks for the double check - $C^\perp(X)$ is indeed $n-p$ dimensional, but we don't see where we mentioned otherwise on page 14. $\mathcal{A}$ is $n-p-1$ dimensional as one degree of freedom is lost for each coefficient estimate and another degree of freedom is lost for the scale estimate.}

@@

Developing an understanding of sources of variation in the data is important.  In settings where the mechanism that produces bad data is stable, we might even entertain building a model for the bad data as is one tradition in Bayesian statistics.  But there are many instances where this is of little interest.

When we are in a situation where (i) and (ii) hold -- we would argue that this is the typical situation and not the exception -- and we have test data available, there would rarely be any reason to believe that the test data would be pure, consisting only of good data.  This is an important motivator of this work as described in the introduction to our paper.

@@

@@

\response{Thanks for pointing out the wish by some to have default choices for $f$ and $T$.  We consider regression analysis to be so fundamental to the discipline of statsitics and to the practice of data analysis that we feel it inappropriate to specify defaults so heavy-handedly.  This would be much like specifying a default likelihood if one wishes to build a regression model.  As you note, choice of the likelihood is part of the analysis when building a Bayesian model.  To this, we add choice of the conditioning statistic $T$ and illustrate the impact of different choices.  Omission of the formal description of the particular M-estimators we use is an oversight.

We have taken the following steps to address your comment:

\begin{enumerate}
\item Point out that M-Estimators have been our default choice in the very first illustrative example:
 \response{Details of these estimators can be found in many places, including \citep{huber2009}. We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers. A short review of these estimators is provided in the Supplementary Material.}
 \item Included a short review of M-Estimators in the Supplement
 \item Included a `Practical Considerations for Using the Restricted Likelihood' to the Supplement. 
\end{enumerate}
}

@@

\response{At the end of section 4 we have included a paragraph:}

\response{'Finally, it is clear the estimators themselves must be computed for every iteration of the Markov Chain. We have found this burden to be marginal relative to computation of the needed Jacobian. In the simulations and real data analyses presented below, we will see that the additional computational expense needed to fit the Bayesian model is often worthwhile, leading to better performance compared to traditional, non-Bayesian robust regression estimators.  This is most evident when substantive prior information is available and information in the data is limited.'}

Additionally, we have included a paragraph in the introduction discussing advantages and disadvantages.
}

@@

\response{To address the concern you have raised, we have changed our evaluation metric in the simulation to a closed form version of KL divergence.  We use the KL divergence between two normals: $ 
\log(\hat\sigma^{2}) - \log(\sigma^{2}) + \frac{1}{\hat\sigma^{2}}(\sigma^{2} + (\theta - \hat{\theta_{i}})^{2}
$
While we wouldn't be able to compute this in a real application, it does combines estimation error for both the $\theta_{i}$ and $\sigma$ and is a decent metric to compare the methods under the simulation setup. }
John - I'm puzzled by this one.  I'll have to check the paper when I get dropbox up and running again.  (Steve)

@@

\response{Thanks for noticing this detail. It is most natural if it is mutually absolutely continuous with respect to the distribution induced by the model on S.  For the cases we discuss, this is mutually absolutely continuous with respect to the uniform distribution on S.  We now mention the importance of the support.  We have also included a description of what we use for p throughout based on a previous comment. This comment is after Theorem 4.6.}
John - a little puzzled by what was intended here.  (Steve)

@@

\response{Thank you - we believe we have addressed each of these concerns based on the the 2 reviewer's comments. Detailed responses are given above.}

@@

\response{We believe we have addressed similar concerns from the two reviewers - specifically we have included in several areas the advantages and disadvantages (e.g., see Introduction) we have found as well as practical recommendations (e.g. See Supplement).}

@@

In contrast, the fractional Bayesian methods do not actually follow Bayes Theorem (there are exceptions in special cases).  The use the theorem as an analogy and so miss many of the benefits of Bayes.  The fractional methods are interesting and they deserve study, but they are not the only solution to Bayesian model misspecification.

In the long run, we suspect that robust and effective Bayesian analyses will make use of ideas from a variety of perspectives that are currently under study.  But the various lines of research need time and effort to develop, and they need visibility for the community to appreciate the perspectives and to develop an understanding of what each brings to the table.}

@@

\section{Editor Comments} \response{unknown response at this point ???}

@@

@@

@@
